Another paper with lots of text and fancy pictures

### 2023-11-27 paper.tex
Extended analysis of the samples

\section{Results}
In this section we compute correlation functions along the plane $XY$ for 2- and
3-dimensional real samples. Table \ref{tab:summary} contains information about
these samples. Note that we compute surface correlation functions only for those
samples for which the criterion $C_{0.5} > 0.97$ holds. Images of the samples
are on \cref{fig:samples}. On plots of correlation functions we provide a family
of curves with the first argument of the correlation function being fixed. For
two highly anisotropic samples (the soil and the shale) we provide heatmaps of
$S_3$ correlation function where anisotropicity can be easily seen. These two
samples was preliminary rotated by $\frac{\pi}{4}$ around the axis $Z$ before
calculation of correlation functions.

Correlation functions for the XCT sample are on
\cref{fig:sample-limestone-cf}. The plot of $S_3$ function allows us to estimate
porosity of the sample to be $\sim 0.04$ (note, that the curve with $r_1 = 0$ is
actually $S_2$ function). The two-point correlation function reaches plateau at
$r_2 \approx 200\div 225\ \mu m$ which means that two events of finding two
points in the void phase are independent if the points are farther than
$225\ \mu m$ from each other. We see that the sample is a little bit anisotropic
($S_3(0, 225) \approx S_3(150, 0)$). From analysis of $C_3$ function it can be
stated that the sample has clusters of void phase which are $\sim 200\ \mu m$ in
diameter.

Correlation functions for the SEM sample are on
\cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
from the plot of $S_3$ function at $r_1 = 0$. The funcion $S_3(0, r_2)$ reaches
plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
diameter.

Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
\cref{fig:heatmaps}.

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale-c3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropicity more visible.}
  \label{fig:heatmaps}
\end{figure*}

>>>>

\section{Results}
In this section we compute correlation functions along the plane $XY$ for 2- and
3-dimensional real samples. Table \ref{tab:summary} contains information about
these samples. Note that we compute surface correlation functions only for those
samples for which the criterion $C_{0.5} > 0.97$ holds (the sandstone and the
limestone). Images of the samples are on \cref{fig:samples}. On plots of
correlation functions we provide a family of curves with the first argument of
the correlation function being fixed. For two highly anisotropic samples (the
soil and the shale) we provide heatmaps of $S_3$ correlation function where
anisotropicity can be easily seen. These two samples was preliminary rotated by
$\frac{\pi}{4}$ around the axis $Z$ before calculation of correlation functions.

Correlation functions for the XCT sample of the limestone are on
\cref{fig:sample-limestone-cf}. The plot of $S_3$ function allows us to estimate
porosity of the sample to be $\sim 0.04$ (note, that the curve with $r_1 = 0$ is
actually $S_2$ function). The two-point correlation function reaches plateau at
$r_2 \approx 200\div 225\ \mu m$ which means that two events of finding two
points in the void phase are independent if the points are farther than
$225\ \mu m$ from each other. We see that the sample is a little bit anisotropic
($S_3(0, 225) \approx S_3(150, 0)$). From analysis of $C_3$ function it can be
stated that the sample has clusters of void phase which are $\sim 200\ \mu m$ in
diameter.

Correlation functions for the SEM sample (the sandstone) are on
\cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
from the plot of $S_3$ function at $r_1 = 0$. The funcion $S_3(0, r_2)$ reaches
plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
diameter.

Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
\cref{fig:heatmaps}. Anisotropicity of the both samples can be seen as a slower
decay of $S_3$ in one of the directions. Additionally, it can be observed that
elongated clusters of the void phase in the sample of soil are parallel to each
other and have a regular spacing about \textcolor{red}{$150 \mu m$}.

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale-c3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropicity more visible. It can be observed that the samples have
    cavities elongated along the vector $(1, 1, 0)$.}
  \label{fig:heatmaps}
\end{figure*}
